Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-21 ms.tex
more clean up, especially in explanation of bandpass corrections

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the SFD 
reprocessing of \IRAS~100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
$6.1'$, and was constructed so as to contain only thermal 
emission from Galactic dust, with compact sources and zodiacal light removed, 
and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as-is, without any 
custom modifications.
%maybe clarify that throughout we use SFD i100 totally as-is, with no
% customization

@@

Our model is that of FDS99, which consists of two populations of dust 
grains emitting as MBBs, but with different temperatures and different 
emissivity power law indices $\beta$. The shape of this spectrum is given by:

@@

At each sky location, we have five independent intensity measurements (four ) 
FDS99 found typical values for $T_2$ and 
%basically just finish clarifying here that we want to start simple by fitting
%only two parameters for each pixel since we only have 5 intensity
% measurements per pixel in our baseline fits at 6.1 arcmin resoluiton

@@

\subsection{Finite Bandpass Correction}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. But in reality
we are comparing to broad bands typically hundreds of GHz wide. The shape of 
model spectrum $M_{\nu}$ is only dependent upon one parameter: the hot
dust temperature $T_2$. We have therefore computed bandpass correction factors
$b_{\nu_i}$ such that $M_{\nu_i}b_{\nu_i}$ is the predicted observation for the
\PLANCK~or \IRAS~band of interest. We have used the \PLANCK~transmission 
curves provided in the file \verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. 
For 3000 GHz, we have used the \IRAS~bandpass, following the treatment of
\cite{planckdust}. We note that it is not clear which bandpass should
properly be ascribed to the \IRAS/DIRBE composite 100$\mu$m maps under
consideration. % (here SFD \verb|i100|) and that of \cite{planckdust}).

>>>>

To incorporate measurements on the Wien side of the dust emission spectrum, 
we include 100$\mu$m data in our SED fits. In particular, we use the SFD 
reprocessing of \IRAS~100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. The \verb|i100| map has angular resolution of 
$6.1'$, and was constructed so as to contain only thermal 
emission from Galactic dust, with compact sources and zodiacal light removed, 
and its zero level tied to H\,\textsc{i}. We use the \verb|i100| map as is, without any 
custom modifications.
%maybe clarify that throughout we use SFD i100 totally as-is, with no
% customization

@@

We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, but with different temperatures 
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

At each sky location, our baseline fit at the full $6.1'$ resolution 
incorporates only five independent intensity measurements (\verb|i100| along 
with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
$T_2$ and

%basically just finish clarifying here that we want to start simple by fitting
%only two parameters for each pixel since we only have 5 intensity
% measurements per pixel in our baseline fits at 6.1 arcmin resoluiton

@@

%mention that we're using healpix in Galactic coordinates !!!!!!

\subsection{Finite Bandpass Correction}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
 of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
nominal band center frequencies for which we have measurements, $\nu_i \in$
\{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum $M_{\nu}$ is only
dependent upon one parameter: the hot dust temperature $T_2$. We have used the 
\PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have 
used the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note 
that it is not clear which bandpass should properly be ascribed to the 
\IRAS/DIRBE composite 100$\mu$m maps under consideration. 
% (here SFD \verb|i100|) and that of \cite{planckdust}).

% introduce nu_i notation in above paragraph with some mention of what it
% means
